Andres Karjus

### 2021-01-12 index.Rmd
news

- [RUSE 2019](http://rusesymposium.org.uk/). Slides [here](https://andreskarjus.github.io/ruse2019).
- [CL2019](http://www.cl2019.org/). Slides [here](https://andreskarjus.github.io/cl2019talk.html).
- [Culture Conference 2019](https://culture-conference.com/programme-2019/), Poster [here](https://andreskarjus.github.io/lexcom_poster).
- [Inaugural ISLE workshop](https://www.comparativelinguistics.uzh.ch/en/events/ISLE-inaugural-workshop.html) | _Modelling lexical interactions in diachronic corpora_ |  [poster](https://andreskarjus.github.io/isle_poster)
- University of Edinburgh [Centre for Language Evolution](http://www.lel.ed.ac.uk/cle/) seminar series | _Challenges in detecting evolutionary forces in language change using diachronic corpora_ | [slides](https://andreskarjus.github.io/evoforces_cletalk/slides.html) | [code](https://github.com/andreskarjus/wfsim_fit)
- Corpus Linguistics in Scotland Network Meeting, _Topical Fluctuations and Lexical Interactions in Diachronic Corpora_

>>>>

-  [Colloquium for Computational Linguistics and Linguistics in Stuttgart](https://www.ims.uni-stuttgart.de/en/research/colloquium/) | [Slides](https://andreskarjus.github.io/talks/stuttgart2021/andres_karjus_lexical_dynamics_slides_stuttgart2021.pdf) | [Recording](https://www.ims.uni-stuttgart.de/documents/aktuelles/veranstaltungen/210111-Karjus-Talk-Colloq-Recording.mp4)
- [RUSE 2019](http://rusesymposium.org.uk/). Slides [here](https://andreskarjus.github.io/ruse2019).
- [CL2019](http://www.cl2019.org/). Slides [here](https://andreskarjus.github.io/cl2019talk.html).
- [Culture Conference 2019](https://culture-conference.com/programme-2019/), Poster [here](https://andreskarjus.github.io/lexcom_poster).
- [Inaugural ISLE workshop](https://www.comparativelinguistics.uzh.ch/en/events/ISLE-inaugural-workshop.html) | _Modelling lexical interactions in diachronic corpora_ |  [poster](https://andreskarjus.github.io/isle_poster)
- University of Edinburgh [Centre for Language Evolution](http://www.lel.ed.ac.uk/cle/) seminar series | _Challenges in detecting evolutionary forces in language change using diachronic corpora_ | [slides](https://andreskarjus.github.io/evoforces_cletalk/slides.html) | [code](https://github.com/andreskarjus/wfsim_fit)
- Corpus Linguistics in Scotland Network Meeting, _Topical Fluctuations and Lexical Interactions in Diachronic Corpora_

### 2021-01-12 news.Rmd
news
postdoc updates

>>>>

- Gave an invited talk about my PhD research on lexical dynamics at the [Colloquium for Computational Linguistics and Linguistics in Stuttgart](https://www.ims.uni-stuttgart.de/en/research/colloquium/). The [Slides](https://andreskarjus.github.io/talks/stuttgart2021/andres_karjus_lexical_dynamics_slides_stuttgart2021.pdf) | [Recording](https://www.ims.uni-stuttgart.de/documents/aktuelles/veranstaltungen/210111-Karjus-Talk-Colloq-Recording.mp4)

- With the corrections approved and paperwork competed, seems I now have a PhD (26.11.2020)

- Was happy to host a job shadow (töövari) student at the CUDAN lab, via the Tagasi Kooli programme (16.11.2020)
